Utilization of Reductions and Abstraction Elimination in Typed Genetic Programming

### 2014-04-11 tex/cec14/article.tex
članky stuff

\author{Tom\'{a}\v{s} K\v{r}en\thanks{Tomáš Křen (tomkren@gmail.cz) is with Charles Univetsity in Prague, Faculty of Mathematics and Physics; Department of Theoretical Computer Science and Mathematical Logic.} \and Roman Neruda\thanks{Roman Neruda (roman@cs.cas.cz) is with Institute of Computer Science, Academy of Sciences of the Czech Republic and has been partially supported by the The Ministry of Education of the Czech Republic project COST LD 13002}}

>>>>

\author{Tom\'{a}\v{s} K\v{r}en\thanks{Tomáš Křen (tomkren@gmail.cz) is with Charles Univetsity in Prague, Faculty of Mathematics and Physics; Department of Theoretical Computer Science and Mathematical Logic \red{and with TODO} and has been partially supported by the project GA ČR P202/10/1333 and by the SVV project number 260~104.} \and Roman Neruda\thanks{Roman Neruda (roman@cs.cas.cz) is with Institute of Computer Science, Academy of Sciences of the Czech Republic and has been partially supported by the The Ministry of Education of the Czech Republic project COST LD 13002.}}

### 2014-04-11 tex/gecco14/gecco14.tex
članky stuff

@@

@@

\maketitle
\begin{abstract}
Lambda calculus representation of programs offers a more expressive alternative to traditional S-expressions. In this paper we discuss advantages of this representation coming from the use of reductions (beta and eta) and a way to overcome disadvantages caused by variables occurring in the programs by use of the abstraction elimination algorithm. We discuss the role of those reductions in the process of generating initial population and propose several crossover approaches, two of which are based on abstraction elimination and compared using the even parity benchmark problem. 
%including novel approach to crossover operator based both on reductions and abstraction elimination. 
%The design goal of this operator is to turn the disadvantage of abstraction elimination  - possibly quadratic increase of program size - into a virtue; our approach leads to more crossover points. At the same time, utilization of reductions provides offspring of small sizes.
\end{abstract}

@@

@@

@@

By generating \lterms in \textit{lnf} we avoid generating 
\lterms $M$,$N$ such that $M \not= N$, but $M =_{\beta\eta} N$.
In other words, we avoid generating two programs with different 
source codes, but performing the same computation.

@@

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}
%This section is optional; it is a location for you to acknowledge grants, funding, editing assistance and what have you.  In the present case, for example, the authors would like to thank Gerald Murray of ACM for his help in codifying this \textit{Author's Guide} and the \textbf{.cls} and \textbf{.tex} files that it describes.

>>>>

\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\def\sharedaffiliation{\end{tabular}\newline\begin{tabular}{c}}

\def\wu{\superscript{*}}
\def\wg{\superscript{\dag}}

@@

\numberofauthors{2}
\author{
  \alignauthor \ Tom\'{a}\v{s} K\v{r}en\wu\wg\\
  \email{tomkren@gmail.com}
  %
  \alignauthor \ Roman Neruda\wu\\
  \email{roman@cs.cas.cz}
  %
  \sharedaffiliation
  \begin{tabular}{ccc}
    \affaddr{{\wu}Institute of Computer Science{\ }}      & & \affaddr{{\wg}Faculty of Mathematics and Physics{\ }} \\
    \affaddr{Academy of Sciences of the Czech Republic}   & & \affaddr{Charles University in Prague} \\
    \affaddr{Pod Vod\'arenskou v\v{e}\v{z}\'\i~2, 18207,} & & \affaddr{Malostransk\'e n\'am\v{e}st\'\i~25, 11000,} \\
    \affaddr{Prague, Czech Republic}                      & & \affaddr{Prague, Czech Republic} \\
  \end{tabular}
}

@@

\maketitle
\begin{abstract}
Lambda calculus representation of programs offers a more expressive alternative to traditional S-expressions. In this paper we discuss advantages of this representation coming from the use of reductions (beta and eta) and a way to overcome disadvantages caused by variables occurring in the programs by use of the abstraction elimination algorithm. We discuss the role of those reductions in the process of generating initial population and propose several crossover approaches, two of which are based on abstraction elimination and compared using the even parity benchmark problem.
\red{Přidat víc o kříženích tak aby davál insight to the project.}
%including novel approach to crossover operator based both on reductions and abstraction elimination. 
%The design goal of this operator is to turn the disadvantage of abstraction elimination  - possibly quadratic increase of program size - into a virtue; our approach leads to more crossover points. At the same time, utilization of reductions provides offspring of small sizes.
\end{abstract}

@@

\red{Zdůraznit že main contribution of this paper je popis crossover operations který [rekapitulovat dobrý vlastnosti našeho křížení z 2ky (a dalších sekcí), tj že to nezjednodušuje na méně obecnou notaci a přesto to zůstává efektivní i v problémech kde to zjednodušení hraje do karet tý metodě.]}

@@

\red{Buď přidat neformální komentář a/nebo odebrat nadbytečný věci.}

@@

By generating \lterms in \textit{lnf} we avoid generating 
\lterms $M$,$N$ such that $M \not= N$, but $M =_{\beta\eta} N$.
In other words, we avoid generating two programs with different 
source codes, but performing the same computation.
\red{Zde potřeba doplnit vysvětlení, že to řeší jen čast tohoto
fenomenu}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

Tomáš Křen has been partially supported by the project GA ČR P202/10/1333 and by the SVV project number 260~104. Roman Roman Neruda has been partially supported by the The Ministry of Education of the Czech Republic project COST LD 13002.

%This section is optional; it is a location for you to acknowledge grants, funding, editing assistance and what have you.  In the present case, for example, the authors would like to thank Gerald Murray of ACM for his help in codifying this \textit{Author's Guide} and the \textbf{.cls} and \textbf{.tex} files that it describes.
